---
title: "NeAtlIBTSR maps"
author: "Fran Velasco"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: false
    theme: yeti
    encoding: {UTF-8}
---

```{r}
library(NeAtlIBTS)

```


## Map of stations in a given survey, year and quarter

* Maps available from the **NeAtlIBTS** package
* This package produces maps from the **HH (& HL)** data in DATRAS
  - Data can be downloaded directly from DATRAS making use of the **icesDATRAS** library, 
  - Or taken from the working directory, where they should be loaded in advance with the DATRAS HH format 

## Maps of stations in a given survey, year and quarter

```{r General Map, fig.width=10.1,fig.height=5.1,include=TRUE,results='hide'}
par(mfrow=c(1,2))
IBTSNeAtl_map(load=F,leg=F)
IBTSNeAtl_map(load=T,leg=T,legpos = "bottomright",cex.leg = .35)
```

## Maps of stations in a given survey, year and quarter

```{r Maps-Survey, fig.cap="Hauls in SCOWCGFS and IE-IGFS IBTS surveys in 2023 4<sup>th</sup> quarter",fig.width=10.1,fig.height=5.1,include=TRUE,results='hide'}
par(mfrow=c(1,2))
SurveyMap.IBTS("SCOWCGFS",2023,4)
SurveyMap.IBTS("IE-IGFS",2023,4)
```

* In the case of the NS-IBTS the function produces a figure with the hauls per country

```{r Maps-Survey NS,fig.cap="North Sea 2023 surveys. 1<sup>st</sup> and 3<sup>rd</sup> quarters", fig.width=18.1,fig.height=10.1,include=TRUE,results='hide'}
par(mfrow=c(1,2))
SurveyMap.IBTS("NS-IBTS",2023,1,legcount = T)
SurveyMap.IBTS("NS-IBTS",2023,3,legcount = T)
```

## There's also a function to get data to produce the data for the IBTS Maps with splitted recruits an adults

* The function SplitLengths gets the data from DATRAS HH and HL and produces a data frame to get the maps with splitted lengths

* Produces a map with the selected species (esp="HAD" in the example) to check that it is working. Function SplitLengthsESP will produce the map for the species and survey, working for only one specie.

```{r Get data for SplitLengths IBTS maps,fig.cap="Whiting distribution in SCOWCGFS 2023 4<sup>th</sup> quarter ",fig.wide=TRUE,include=TRUE,results='hide'}
SplitLengths(datSurvey ="SCOWCGFS",dtyear= 2023,dtq=4,esp = "HAD",plot=T,out.dat = FALSE)
```

* The list of species included and the length split parameters are taken from file **SpeciesCodes** part of the **NeAtlIBTS** package, the **lengthsplit** value gives the split limit between small and large, it is in cm but converted to mm during the split lengths process

```{r File original to Get data for SplitLengths IBTS maps,fig.width=10.1,fig.height=10.1,include=TRUE,results='show'}
head(SpeciesCodes)
```

* the function also produces the data for the whole set of species (in present in the survey)

```{r File produced by SplitLengths with only the survey selected,include=TRUE,results='show'}
head(dplyr::filter(SplitLengths("SCOWCGFS",2023,4,plot=F,out.dat=T),Survey=="SCOWCGFS"))
```

* The function **SplitLengthsESP** produces from DATRAS HH and HL **records** the map of distribution of one species in a survey (year and quarter) with two length ranges (or just one if L_Split=NA)

```{r PTIBTS map,fig.cap="PT-IBTS hake large and small distribution. 2023 4<sup>th</sup> quarter",fig.wide=T,include=TRUE,results='show'}
SplitLengthsESP(datSurvey = "PT-IBTS",dtyear=2023,dtq=4,L_Split = 20,esp="Merluccius merluccius",legpos = "bottomleft")
```