---
title: "NeAtlIBTSR"
author: "Fran Velasco"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: yeti
    encoding: {UTF-8}
---

```{r}
library(NeAtlIBTS.R)

```

### Plots of gear behaviour from the NorthEastern Atlantic IBTS

* Graphs available from the HH DATRAS files
* This package produces figures of the different parameters of the gear behaviour in relation to Depth and between them.
  - Data can be downloaded directly from DATRAS making use of the icesDATRAS library, 
  - Or taken from the working directory, where they should be loaded in advance with the DATRAS HH format 
  - Default colors are dark blue for the depth, and steelblue for the shallower depths.


## Warp vs Depth graphs

```{r Warp-Depth, fig.width=10.1,fig.height=5.1,include=TRUE,results='hide'}
par(mfrow=c(1,2))
gearPlotHH.wrpdp("SWC-IBTS",c(2011:2016),1,col1="darkblue")
gearPlotHH.wrpdp("SWC-IBTS",c(2011:2016),1,col1="darkblue",pF=F)
```

* pF option hides the points and leaves the curves to remark gear behaviour
* You can download the data for the years selected using the function getHHdata.ts

```{r Get data,include=TRUE,results='hide'}
ieigfs<-getHHdata.ts(Survey="IE-IGFS",years=c(2011:2016),quarter=4)
```


## Door spread vs depth graphs

* Once downloaded the data we can produce plots and format them without downloading again

```{r DoorSpread, fig.width=10.2,fig.height=5.1,include=TRUE,results='hide',fig.align='left',echo=FALSE,message=FALSE}
par(mfrow=c(1,2))
gearPlotHH.dodp(ieigfs,years=c(2011:2016),quarter=4,getICES = FALSE)
gearPlotHH.dodp(ieigfs,c(2011:2016),4,pF=F,getICES=F)
```


## Wing spread vs depth graphs

```{r WingSpread, fig.width=10,fig.height=4.1,fig.align='left',include=TRUE,results='hide',echo=FALSE,message=FALSE}
par(mfrow=c(1,2))
gearPlotHH.wgdp("EVHOE",c(2011:2016),4,.3)
gearPlotHH.wgdp("EVHOE",c(2011:2016),4,.4,pF=F)
```

## Net opening (Vertical) vs depth graphs

```{r NetOpening,echo=FALSE,fig.align='center', fig.width=10, fig.height=4.1,include=TRUE,results='hide',message=FALSE}
par(mfrow=c(1,2))
gearPlotHH.nodp("SP-PORC",c(2011:2016),3,.3)
gearPlotHH.nodp("SP-PORC",c(2011:2016),3,.4,pF=F)
```

## Door spread vs Wing spread graphs

```{r DoorSpread vs WingSpread, fig.width=10, fig.height=4.1,include=TRUE,results='hide'}
par(mfrow=c(1,2))
gearPlotHH.wgdo("SP-ARSA",c(2014:2016),1,col1="darkblue",col2="steelblue2")
gearPlotHH.wgdo("SP-ARSA",c(2014:2016),1,col1="darkblue",col2="steelblue2",pF=F)
```
